\MakeUppercase{The Structure of $k$-Planar Graphs}

### 2020-03-25 k-planar.tex
Did comments by referee 1

We prove the following theorem that shows if a graph $G$ is a subgraph of $H\boxtimes P$ and $\PP$ is a shortcut system for $G$, then $G^{\mathcal{P}}$ is a subgraph of $J\boxtimes P$, where the treewidth of $J$ is bounded by a function of $k$, $d$, and the treewidth of $H$.

@@

\begin{lem}\lemlabel{nice-decomposition}
  For every graph $H$ of treewidth $t$, there is a rooted tree $T$ with $V(T)=V(H)$ and a width-$t$ $T$-decomposition $(B_x:x\in V(T))$ of $H$ that has following additional properties:
  \begin{compactenum}[(T1)]
    % \item\tlabel{rooted}\tlabel{first} $T$ is rooted at some node $x_0\in V(T)$ with $B_{x_0}=\emptyset$.
    % \item\tlabel{node-set} $V(T)= V(H)$.
    % \item\tlabel{diff} For each edge $xy\in E(T)$, $|B_x\ominus B_y|\le 1$.
    \item\tlabel{subtree-root} For each node $x\in V(H)$, the subtree $T[x]:=T[\{y\in V(T):x\in B_y\}]$ is rooted at $x$.
    \item\tlabel{ancestor-edge}\tlabel{last} For each edge $xy\in E(H)$, one of $x$ or $y$ is a $T$-ancestor of the other.
  \end{compactenum}
\end{lem}

>>>>

We prove the following theorem that shows if a graph $G$ is a subgraph of $H\boxtimes P$ and $\PP$ is a $(k,d)$-shortcut system for $G$, then $G^{\mathcal{P}}$ is a subgraph of $J\boxtimes P$, where the treewidth of $J$ is bounded by a function of $k$, $d$, and the treewidth of $H$.

@@

\begin{lem}\lemlabel{nice-decomposition}
  For every graph $H$ of treewidth $t$, there is a rooted tree $T$ with $V(T)=V(H)$ and a width-$t$ $T$-decomposition $(B_x:x\in V(T))$ of $H$ that has following additional properties:
  \begin{compactenum}[(T1)]
    % \item\tlabel{rooted}\tlabel{first} $T$ is rooted at some node $x_0\in V(T)$ with $B_{x_0}=\emptyset$.
    % \item\tlabel{node-set} $V(T)= V(H)$.
    % \item\tlabel{diff} For each edge $xy\in E(T)$, $|B_x\ominus B_y|\le 1$.
    \item\tlabel{subtree-root} for each node $x\in V(H)$, the subtree $T[x]:=T[\{y\in V(T):x\in B_y\}]$ is rooted at $x$; and consequently
    \item\tlabel{ancestor-edge}\tlabel{last} for each edge $xy\in E(H)$, one of $x$ or $y$ is a $T$-ancestor of the other.
  \end{compactenum}
\end{lem}
